\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-16 tex/paper.tex
Added some introductions

\fix Clarify problem definition and research questions
\newpage
\section{Background}
\subsection{About Uprise}
Uprise (formerly known as ESN) is a company based in Uppsala, Sweden. It is an EA studio focussing 
on creating great gaming experiences, which means that they are mostly not focussed on the actual 
gameplay which other EA studios like DICE is. Currently Uprise has a lot of focus on developing 
companion apps and a new form of menu systems.

@@

\newpage
\section{Related Terminology}
In this section concepts and abbreviations, that are recurring throughout the paper, which the
reader needs to be familiar with are explained.

\subsection{Abbreviations}
\subsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source
licence, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and dead locks.

\subsubsection{CDN}
Content Distribution/Delivery Network - Replicates content to several servers, usually spread out
geographically. Once a request is made, the network serves content from the server closest to the
requester.

\subsection{Terms}
\subsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with a full copy of a system, or part of a system, as full copies 
can be used as backups meanwhile snapshots are not very effective means of backup in the case of 
data corruption. It is not effective against data corruption as snapshots usually still refer to 
unchanged data that is still a part of the system~\cite{SNAPSHOT}.

\subsubsection{Eventual Consistency}
The expression eventual consistency is a term used for describing how data is processed. It is often
used in the context of database systems. Eventual consistency means that stored data is guaranteed 
to be consistent in any one moment, but at some point the data will eventually converge to being 
consistent~\cite{EVENTUAL}.

@@

@@

\subsection{Approach}
\fix Write about how the approach is similar to BLP and that it is not a proof etc

As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the design of the system.

@@

\newpage
\section{Implementation} \label{sec:implementation}
This chapter deals with the second part of this work, namely the implementation of the Perius 
system based which is based on the model described in Section~\ref{sec:model}. As this work is not
intended as a instructions manual more information about how to deploy and use Perius can be found
on \url{http://perius.se}. This chapter's focus is instead on how the decisions for the
implementation were made, how well the system would scale and the resulting security implications.

\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

In the current system you can only upload a file once as there will be a collision in the upload
otherwise, as the old and the new file will have the same MD5 hash.

@@

\fix Insert more systems here

@@

The service features a virtual file structure over the assets that has been stored, snapshots,
security management of whole containers as well as individual files, audit and access logging, multi
project support and a modular design for persistent storage.

@@

Running 2m test @ http://perius:8000/static
  100 threads and 100 connections
  Thread Stats   Avg      Stdev     Max   +/- Stdev
    Latency     6.42ms   28.99ms 290.37ms   96.26%
    Req/Sec     0.94k   203.30     2.00k    83.83%
  9199737 requests in 1.67m, 2.19GB read
Requests/sec:  91902.48
Transfer/sec:     22.44MB
\end{lstlisting}
\end{minipage}

@@

\par
These are very simple requests, to evaluate how much load the application can handle in its current
state a more complex but common request has to be analysed. The most complicated and still common
request that system is receiving is requests of a full project tree. This request is computationally
expensive as the tree is not stored directly in the database but has to be built from the id and
parent id of each container and content, a simulated project tree of similar size to the ones stored 
in the current management system reaches around 25KB in uncompressed size.
\end{custommargins}

@@

\par
Another simple optimisation that was added was indices on the parent id's, which are heavily queried
when building the project trees.

@@

\subsubsubsection{Serving private content} \label{sec:private_content}
There are three different ways, that this implementation make use of, to make sure that the CDNs
serve content in a private manner. The first two are signed URLs and signed cookies, and the third
is a mixture between one of the first two together with a range of IP addresses.~\cite{AWSPRIVATE}
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that assets
are not leaked if an attacker manages to find out the URL for the asset.

@@

%What to write about
%Battle Binary
%Security features of CDN's
%What is needed by the logic, like what happens after two consecutive deletes
%
%What is needed
%* Security layers
%* snapshots
%* Virtual file structure
%* Versioning of content
%* Multi project support
%* Auth and audit logs
%* Users

>>>>

\fix Clarify problem definition and research questions
\newpage
\section{Background}
This section gives the reader some background of the company which the thesis was done at and
explanation of the core concepts which are exerted.

\subsection{About Uprise}
Uprise (formerly known as ESN) is a company based in Uppsala, Sweden. It is an EA studio focussing 
on creating great gaming experiences, which means that they are not focussed on the actual 
gameplay, which other EA studios like DICE are. Currently Uprise has a lot of focus on developing 
companion apps and a new form of menu systems.

@@

\newpage
\subsection{Related Terminology}
In this section concepts and abbreviations, that are recurring throughout the paper, which the
reader needs to be familiar with are explained.

\subsubsection{Abbreviations}
\subsubsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source
licence, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and dead locks.

\subsubsubsection{CDN}
Content Distribution/Delivery Network - Replicates content to several servers, usually spread out
geographically. Once a request is made, the network serves content from the server closest to the
requester.

\subsubsection{Terms}
\subsubsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of, at a certain time.
Snapshots should not be confused with a full copy of a system, or part of a system, as full copies 
can be used as backups meanwhile snapshots are not very effective means of backup in the case of 
data corruption. It is not effective against data corruption as snapshots usually still refer to 
unchanged data that is still a part of the system~\cite{SNAPSHOT}.

\subsubsubsection{Eventual Consistency}
The expression eventual consistency is a term used for describing how data is processed. It is often
used in the context of database systems. Eventual consistency means that stored data is guaranteed 
to be consistent in any one moment, but at some point the data will eventually converge to being 
consistent~\cite{EVENTUAL}.

@@

%\subsubsubsection{Perius}
%Perius is the name of the implementation that was made during this project. It is an anagram of
%Uprise and also a type of butterfly.

@@

\subsection{Approach}
As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the design of the system.

@@

\newpage 
\section{Implementation} \label{sec:implementation} 
This chapter deals with the second part of this work, namely the implementation of the Perius system
based which is based on the model described in Section~\ref{sec:model}. As this work is not intended
as an instructions manual, more information about how to deploy and use Perius can be found on
\url{http://perius.se}. This chapter's focus is instead on how the decisions for the implementation
were made, how well the system would scale and the resulting security implications.

\subsection{Background}
\subsubsection{The current system} \label{sec:current_system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use of the
security features that the CDNs are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

In the current system you can only upload a file once as there will be a collision in the upload
otherwise, as the old and the new file will have the same MD5 hash, which is by design as duplicate
content just wastes space on the CDN. The problem with this is that the current interface does not
handle it very well as one file can not be shown or uploaded in two different places in the virtual
filesystem.

@@

\fix Insert more systems here and add a comparison of the systems

@@

The service features a virtual file structure over the assets that has been stored, snapshots,
security management of whole containers as well as individual files, audit and auth logging, multi
project support and a modular design for persistent storage.

@@

Running 2m test @ http://perius:8000/static
  100 threads and 100 connections
  Thread Stats   Avg      Stdev     Max   +/- Stdev
    Latency     6.42ms   28.99ms 290.37ms   96.26%
    Req/Sec     0.94k   203.30     2.00k    83.83%
  9199737 requests in 1.67m, 2.19GB read
Requests/sec:  91902.48
Transfer/sec:     22.44MB
\end{lstlisting}
\end{minipage}
\end{custommargins}

@@

\par These are very simple requests, to evaluate how much load the application can handle in its
current state a more complex but common request has to be analysed. The most complicated and still
common request that system is receiving is requests of a full project tree. This request is
computationally expensive as the tree is not stored directly in the database but has to be built
from the id and parent id of each container and content, a simulated project tree of similar size to
the ones stored in the current management system reaches around 25KB in uncompressed size.

@@

\par
Another simple optimisation that was added was indices on the parent ids, which are heavily queried
when building the project trees.

@@

\subsubsubsection{Serving private content} \label{sec:private_content}
There are three different ways, that this implementation make use of, to make sure that the CDNs
serve content in a private manner. The first two are signed URLs and signed cookies, and the third
is a mixture between one of the first two together with a range of IP addresses.~\cite{AWSPRIVATE}
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that assets
are not leaked if an attacker manages to find out the URL for the asset. \\

@@

%What to write about
%Battle Binary
%Security features of CDNn's
%What is needed by the logic, like what happens after two consecutive deletes
%
%What is needed
%* Security layers
%* snapshots
%* Virtual file structure
%* Versioning of content
%* Multi project support
%* Auth and audit logs
%* Users
